%-------------------------
% Resume in Latex
% Author : Marcus Hedlund (based on Jake's Resume)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%ADJUST HERE
% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingMasters}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Marcus Hedlund} \\ \vspace{1pt}
    \small
(612) 669-2313 $|$ \href{mailto:mhedlund@seas.upenn.edu}{\underline{mhedlund@seas.upenn.edu}} $|$ 
    \href{http://linkedin.com/in/marcushedlund}{\underline{linkedin.com/in/marcushedlund}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingMasters
      {University of Pennsylvania}{Philadelphia, PA}
      {Bachelor of Science in Engineering in Artificial Intelligence; GPA: 4.00/4.00}{May 2027}{Master of Science in Engineering in Computer and Information Science; GPA: 4.00/4.00}{May 2027}
    \resumeSubheading
      {The Blake School}{Minneapolis, MN}
      {High School Diploma; GPA: 3.98/4.00; ACT: 36}{June 2023}
      \resumeItemListStart
        \resumeItem{Sarah Armfield-Hill Award in Mathematics; Cum Laude Society; U.S. Presidential Scholar Candidate}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------RELEVANT COURSEWORK-----------
\section{Relevant Coursework}

 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Computer Science Foundations}{: Programming Languages and Techniques II, Introduction to Algorithms, Interactive Computer Graphics, Signal and Information Processing, Automata, Computation, and Complexity} \\
     \textbf{Artificial Intelligence}{: Artificial Intelligence, Machine Learning, Algorithmic Game Theory, Judgment and Decisions} \\
     \textbf{Systems}{: Database and Information Systems, Internet and Web Systems,  Operating Systems} \\
     \textbf{Mathematics}{: Mathematical Foundations of Computer Science, Calculus Part III (Multivariable Calculus), Probability} \\
     % \textbf{Libraries}{: NumPy, pandas, Matplotlib}
    }}
 \end{itemize}
 
 % \begin{itemize}[leftmargin=0.15in, label={}]
 %    \small{\item{
 %     \textbf{Computer Science}{: Programming Languages and Techniques II, Introduction to Computer Systems, Introduction to Algorithms, } \\
 %     \textbf{Artificial Intelligence}{: Artificial Intelligence, Machine Learning, Algorithmic Game Theory} \\
 %     \textbf{Systems}{: Introduction to Computer Systems, Database and Information Systems, Internet and Web Systems,  Operating Systems Design and Implementation} \\
 %     \textbf{Mathematics}{: Mathematical Foundations of Computer Science, Automata, Computation, and Complexity, Calculus, Part III (Multivariable Calculus, Probability} \\
 %     \textbf{Miscellaneous}{: Signal and Information Processing,  Interactive Computer Graphics, Judgment and Decisions, 3D Computer Modeling} \\
 %     % \textbf{Libraries}{: NumPy, pandas, Matplotlib}
 %    }}
 % \end{itemize}

  % \resumeSubHeadingListStart
  
  %   \resumeItem{
  %   % \textbf{Current:}
  %   CIS 4480 - Operating Systems Design and Implementation, CIS 4600 - Interactive Computer Graphics, ESE 2240 - Signal and Information Processing, NETS 4120 - Algorithmic Game Theory, PSYC 2737 - Judgment and Decisions}
  % \resumeSubHeadingListEnd
% 
%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{Cloud-based Search Engine} $|$ \emph{CIS 5550 Final Project; Java}}{Nov. 2024 -- Dec. 2024}
    \resumeItemListStart
      \resumeItem{Collaborated in a 4-person team to develop a distributed search engine processing 150,000+ web pages. Process included designing a web server, web crawler, distributed kvs, analytics engine, ranker, and frontend.}
      \resumeItem{Designed sophisticated database architecture with reverse indexing, PageRank calculation, and word frequency and meta data tracking stored using AWS Dynamo DB and S3 for improved scalability and latency.}
      \resumeItem{Implemented optimization techniques to enhance search quality and performance including Porter stemming, domain deduplication, intelligent caching strategies, and multi-factor ranking.}
      \resumeItem{Engineered URL filtering to crawl only high-quality HTTPS pages with strict latency and length constraints.}
    \resumeItemListEnd
    
    \resumeProjectHeading{\textbf{Music Exploration Web Application} $|$ \emph{CIS 5500 Final Project; JavaScript}}{Sept. 2024 -- Dec. 2024}
    \resumeItemListStart
      \resumeItem{Developed a full-stack music analytics platform in a 4-person team using React, Node.js, and PostgreSQL, integrating Spotify, Billboard, and Kaggle datasets to provide comprehensive music industry insights.}
      \resumeItem{Optimized complex database queries, reducing query runtimes from up to a minute to under a second through strategic indexing, caching, and query restructuring.}
    \resumeItem{Created advanced analytics capabilities, including visualizations of audio feature evolution, chart performance tracking, artist similarity recommendations, and curated lists of trending songs, rising artists, and top charters.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{Leadership Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Developer}{Philadelphia, PA}
      {UPGRADE}{Sept. 2023 -- Present}
        \resumeItemListStart
        \resumeItem{Collaborated in various small teams to develop game elements such as interactive UI/UX for a game's management system and a 2D boss-fight platformer with interactive objects, parallax effects, and custom animations.}
        \resumeItem{Hosted game jams and speaker events with professors and industry leaders, including Mobius Digital.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Member}{Philadelphia, PA}
      {SIGGRAPH}{Sept. 2023 -- Present}
      \resumeItemListStart
      \resumeItem{Conducted weekly project showcases, providing constructive technical feedback to improve members' skills.}
      \resumeItem{Evaluated hands-on workshops exploring the graphics pipeline including texturing, lighting, and shaders.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C, C++, C\#, OCaml, SQL (PostgreSQL), JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, PyTorch, Unity} \\
     \textbf{Developer Tools}{: Git, AWS, LaTeX} \\
     \textbf{Libraries}{: NumPy, pandas, Matplotlib}
    }}
 \end{itemize}

%-------------------------------------------

%-----------Additional Information-----------
\section{Additional Information}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Dual Citizenship}{: Swedish and American} \\
     \textbf{Swiss Semester}{: Skied, wet-gorged, ice-climbed, and studied abroad in Zermatt, Switzerland} \\
     \textbf{Other}{: Avid hockey player, high school varsity soccer captain, and dedicated pianist}}}
 \end{itemize}

%-------------------------------------------
\end{document}
